Unsupervised training of maximum-entropy models for lexical selection in rule-based machine translation

### 2015-02-18 2015-eamt-melsa/2015-eamt-melsa.tex
fixes
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58997 72bbbca6-d526-0410-a7d9-f06f51895060

 Evaluation results are presented in 
%tables~\ref{table:eval-para-results} and \ref{table:eval-mono-results}.
 table \ref{table:eval-mono-results}, which compares the results of
 the new approach with respect to the \emph{default behaviour} (the
 linguist-chosen defaults,\footnote{The high error rate
   for the Breton--French pair may be as a result of having the
   linguistic defaults tuned to a different domain than that of the
   corpus.}  with respect to the \emph{oracle} (which represents the
 upper bound to performance), and with respect to the results obtained
 by using the target-language model online, for each of the language
 pairs in Apertium with respect to our two evaluation metrics.
 Significant improvements with respect to the results obtained using
 the target-language model online are apparent with the Breton--French
 ---the pair with the least data--- and the English--Spanish language
 pairs. In the remaining cases, the maximum-entropy method comes close
 to the target-language model performance, at a much smaller
 computational cost.\todo{I miss a brief separate discussion of BLEU and LER, which are reported separately!}

>>>>

 Evaluation results are presented in 
%tables~\ref{table:eval-para-results} and \ref{table:eval-mono-results}.
 table \ref{table:eval-mono-results}, which compares the results of
 the new approach with respect to the \emph{default behaviour} (the
 linguist-chosen defaults,\footnote{The high error rate
   for the Breton--French pair may be as a result of having the
   linguistic defaults tuned to a different domain than that of the
   corpus.}  with respect to the \emph{oracle} (which represents the
 upper bound to performance), and with respect to the results obtained
 by using the target-language model online, for each of the language
 pairs in Apertium with respect to our two evaluation metrics.
 Significant improvements with respect to the results obtained using
 the target-language model online are apparent with the Breton--French
 ---the pair with the least data--- and the English--Spanish language
 pairs. In the remaining cases, the maximum-entropy method comes close
 to the target-language model performance in terms of similar or better BLEU and LER scores, at a much smaller
 computational cost.
% \todo{I miss a brief separate discussion of BLEU and LER, which are reported separately!}
